---
title: "Project"
author: ""
date: "2023-12-11"
output:   
  flexdashboard::flex_dashboard:
    orientation: rows
    social: ["wechat"]
    theme: united
    source_code: embed
---

```{r setup, include=FALSE}
library(ggplot2)
library(plotly)
library(dplyr)
library(stringr)
library(tidyr)
library(flexdashboard)
library(knitr)
library(tidyverse)
library(purrr) # for functional programming
library(ggwordcloud) # for creating word cloud
library(crosstalk)
```

```{r}
df <- read.csv("data/netflix_titles.csv")
```


# Video Types {.storyboard}
### Total prevalence type & Total production quantity 
```{r}
data <- df %>% mutate(release_year = as.numeric(str_sub(release_year, -4))) # get years
data <- data %>% separate_rows(listed_in, sep = ", ") %>% # Separate the listed in lines by commas
  arrange(release_year) # Sort by year
```

```{r}
# Statistics of the top ten quantity types each year
top10_types <- data %>%
  group_by(release_year, listed_in) %>%
  summarise(type_count = n()) %>%
  arrange(release_year, desc(type_count)) %>%
  group_by(release_year) %>%
  top_n(10)

# top10_types
```

```{r}
# List number of times
grouped_table <- top10_types %>%
  group_by(listed_in) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```


```{r}
colnames(grouped_table) <- c("Type_name", "epidemic_years")

p1 <- ggplot(data = grouped_table, mapping = aes(
  x = reorder(Type_name, -epidemic_years),
  y = epidemic_years, fill = epidemic_years
)) +
  geom_bar(stat = "identity") +
  scale_fill_gradient(low = "#221f1f", high = "#b20710") + # Set color gradient
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Total prevalence type", x = "type", y = "The number of epidemic years of a type")

ggplotly(p1)
```

```{r}
total_table <- top10_types %>%
  group_by(listed_in) %>%
  summarise(total_count = sum(type_count), .groups = "drop")

# total_table

# The summary table is arranged according to the number of occurrences from largest to smallest
total_table <- total_table %>% arrange(desc(total_count))
# colnames(total_table) <- c("Type name", "List times")

# total_table
```

### Total prevalence type & Total production quantity 
```{r}
colnames(total_table) <- c("Type_name", "Production_volume")
# Summary of the number of production types
p2 <- ggplot(data = total_table, mapping = aes(
  x = reorder(Type_name, -Production_volume),
  y = Production_volume, fill = Production_volume
)) +
  geom_bar(stat = "identity") +
  scale_fill_gradient(high = "#b20710", low = "#221f1f") + # Set color gradient
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Total production quantity", x = "type", y = "Production volume")

ggplotly(p2)
```


Duration
============================

Row
-------------------

### Movie Duration  vs. Decade

```{r}
data <- subset(df, type == "Movie")
data$duration <- as.numeric(str_extract(data$duration, "\\d+"))

data$decade <- cut(data$release_year, breaks = seq(1920, 2040, by = 10), labels = seq(1920, 2030, by = 10))

ggplot(data %>% filter(duration <= 200), aes(x = decade, y = duration)) +
  geom_boxplot(fill = "#b20710", color = "#221f1f", notch = TRUE) +
  labs(
    title = "Duration Distribution of Movies by Decade",
    x = "Decade",
    y = "Duration"
  ) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 200, 50), labels = paste0(seq(0, 200, 50), " minutes"))
```

### TV Show Duration  vs. Decade

```{r}
data <- subset(df, type == "TV Show")
data$duration <- as.numeric(str_extract(data$duration, "\\d+"))

data$decade <- cut(data$release_year, breaks = seq(1920, 2040, by = 10), labels = seq(1920, 2030, by = 10))

ggplot(data, aes(x = decade, y = duration)) +
  geom_boxplot(fill = "#b20710", color = "#221f1f", notch = TRUE) +
  labs(
    title = "Duration Distribution of TV Show by Decade",
    x = "Decade",
    y = "Duration"
  ) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 20, 5), labels = paste0(seq(0, 20, 5), " seasons"))
```

Row
-------------------

### Movie Duration  vs. Genre

```{r}
data <- df %>%
  filter(type == "Movie") %>%
  mutate(duration = as.numeric(str_extract(duration, "\\d+"))) %>%
  separate_rows(listed_in, sep = ", ") %>%
  group_by(listed_in) %>%
  summarise(avg_duration = mean(duration, na.rm = TRUE))

ggplot(data, aes(x = reorder(listed_in, avg_duration), y = avg_duration, fill = avg_duration)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Duration of Movies by Genre",
    x = "Genre",
    y = "Average Duration (minutes)",
    fill = "Average Duration (minutes)"
  ) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 150, 20), labels = seq(0, 150, 20)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip() +
  scale_fill_gradient(low = "#221f1f", high = "#b20710")
```

### TV Show Duration  vs. Genre

```{r}
data <- df %>%
  filter(type == "TV Show") %>%
  mutate(duration = as.numeric(str_extract(duration, "\\d+"))) %>%
  separate_rows(listed_in, sep = ", ") %>%
  group_by(listed_in) %>%
  summarise(avg_duration = mean(duration, na.rm = TRUE))

# 绘制图表
ggplot(data, aes(x = reorder(listed_in, avg_duration), y = avg_duration, fill = avg_duration)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Average Duration of TV Shows by Genre",
    x = "Genre",
    y = "Average Duration (seasons)",
    fill = "Average Duration (seasons)"
  ) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 7, 1), labels = seq(0, 7, 1)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  coord_flip() +
  scale_fill_gradient(high = "#221f1f", low = "#b20710")
```

Rating
=====================================
## Column {.tabset data-width="650"}
```{r include=FALSE}
mydata <- df[df$rating != "", ]

l <- unique(mydata$rating)
l

plotdata <- mydata %>%
  group_by(rating) %>%
  summarize(n = n())
plotdata
```
### The rating category under different type

```{r}
plotdata <- mydata %>%
  group_by(type, rating) %>%
  summarize(n = n())

category_type_data <- plotdata %>%
  mutate(category = case_when(
    rating %in% c("G", "TV-G", "TV-Y") ~ "Little Kids",
    rating %in% c("PG", "TV-PG", "TV-Y7") ~ "Older Kids",
    rating %in% c("TV-Y7-FV", "PG-13", "TV-14") ~ "Teenagers",
    rating %in% c("NC-17", "NR", "R", "TV-MA", "UR") ~ "Adults",
    TRUE ~ "Other" # Add a default category for any unexpected ratings
  ))


category_type_data$category <- factor(category_type_data$category,
  levels = c("Little Kids", "Older Kids", "Teenagers", "Adults"),
  ordered = TRUE
)

p <- category_type_data %>%
  ggplot(aes(rating, n, fill = type, label = n)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(position = position_stack(vjust = 0.5), color = "white", size = 3) +
  labs(x = "Rating", y = "Count", title = "Distribution of Ratings with Type") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    strip.text.x = element_text(margin = margin(b = 10)),
    legend.position = "right"
  ) +
  facet_grid(. ~ category, scales = "free_x", labeller = label_both) +
  scale_fill_manual(values = c("#b20710", "#221f1f")) +
  theme(
    panel.border = element_rect(color = "black", fill = NA, size = 1)
  )
ggplotly(p)
```

### rating catergory over each year
```{r}
plotdata <- mydata %>%
  mutate(category = case_when(
    rating %in% c("G", "TV-G", "TV-Y") ~ "Little Kids",
    rating %in% c("PG", "TV-PG", "TV-Y7") ~ "Older Kids",
    rating %in% c("TV-Y7-FV", "PG-13", "TV-14") ~ "Teenagers",
    rating %in% c("NC-17", "NR", "R", "TV-MA", "UR") ~ "Adults",
    TRUE ~ "Other" # Add a default category for any unexpected ratings
  )) %>%
  group_by(category, release_year) %>%
  summarize(n = n()) %>%
  group_by(release_year) %>%
  mutate(prop = round((n / sum(n)) * 100, 1))  %>%
  as.data.frame()

p3 <- plotdata %>%
  filter(release_year >= 2000) %>%
  ggplot(aes(release_year, prop, fill = category)) +
  geom_bar(stat = "identity", position = "fill") +
  geom_text(aes(label = paste0(prop, "%")),
            position = position_fill(vjust = 0.5), 
            color = "white", 
            size = 3) +  # Add text labels with percentages
  scale_y_continuous(labels = scales::percent_format(scale = 100)) +
  labs(
    x = "Release Year",
    y = "Count (Percentage)",
    title = "Distribution of Ratings Over Years"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = c("#221f1f", "#5e4d4d", "#b20710", "#ec8b06"))

p3_plotly <- ggplotly(p3)
p3_plotly
```

### The distribution of rating
```{r}
### The distribution of rating
plotdata <- mydata %>%
  group_by(rating) %>%
  summarize(n = n())

# bar chart with rotated labels
p1 <- ggplot(
  plotdata,
  aes(
    x = reorder(rating, -n),
    y = n,
    fill = rating
  )
) +
  geom_bar(stat = "identity") +
  labs(
    x = "Rating",
    y = "Count",
    title = "The distribution of rating"
  ) +
  theme(axis.text.x = element_text(
    angle = 45,
    hjust = 1
  )) +
  scale_fill_manual(values = c(
    "#221f1f", "#301D1C", "#3E1B1B", "#4C1919", "#5A1717",
    "#681515", "#761313", "#841111", "#921010", "#A00E0E",
    "#AE0C0C", "#BC0A0A", "#CA0808", "#B20710", "#b20710", "#ec8b06", "#ec8b90"
  ))
p1_plotly <- ggplotly(p1)
p1_plotly
```

### Trend of Ratings Categories Over Years
```{r}
l_category_type_plot_data <- mydata %>%
  mutate(category = case_when(
    rating %in% c("G", "TV-G", "TV-Y") ~ "Little Kids",
    rating %in% c("PG", "TV-PG", "TV-Y7") ~ "Older Kids",
    rating %in% c("TV-Y7-FV", "PG-13", "TV-14") ~ "Teenagers",
    rating %in% c("NC-17", "NR", "R", "TV-MA", "UR") ~ "Adults",
    TRUE ~ "Other" # Add a default category for any unexpected ratings
  )) %>%
  group_by(category, release_year) %>%
  summarize(n = n()) %>%
  group_by(release_year) %>%
  mutate(prop = round((n / sum(n)) * 100, 1))  %>%
  as.data.frame()


gg <- l_category_type_plot_data %>%
  filter(release_year >= 2000) %>%
  ggplot(aes(x = release_year, 
             y = prop, 
             color = category, 
             group = category,
             text = paste("Category: ", category, "<br>Prop: ", prop))) +
  geom_line(size = 1.5) +  
  geom_point(size = 3, alpha = 0.7) +  
  labs(x = "Release Year", 
       y = "Percentage",
       title = "Trend of Ratings Categories Over Years") +
  scale_y_continuous(labels = scales::percent_format(scale = 1), limits = c(0, 100)) +
  scale_color_manual(values = c("#221f1f", "#5e4d4d","#b20710", "#ec8b06")) + # Use scale_color_manual for line colors
  theme_minimal() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~category, scales = "free_y")  # Split the plot by category

# Use ggplotly to make it interactive
ggplotly(gg)

```

Country
=====================================
## Column {.tabset data-width="650"}

### Country vs Types
```{r}
# Pre-process
df <- read.csv("data/netflix_titles.csv", na.strings = c("", "NA"))

grouped <- df %>%
  filter(!is.na(country) & country != "") %>% # remove the NA country
  filter(!is.na(date_added)) %>% # remove the NA date_added
  mutate(year_added = year(parse_date(date_added, "%B %d, %Y"))) %>% # extract year_added
  mutate(country = strsplit(as.character(country), ",")) %>%
  mutate(country = lapply(country, trimws)) %>%
  unnest(country) %>%
  group_by(country, year_added, type) %>%
  summarise(cnt = n()) %>%
  filter(!is.na(country) & country != "")

country_accum <- grouped %>%
  group_by(country, year_added) %>%
  summarise(cnt = sum(cnt)) %>%
  group_by(country) %>%
  arrange(year_added) %>%
  mutate(accum = cumsum(cnt))

by_country_type <- grouped %>%
  group_by(country, type) %>%
  summarise(cnt = sum(cnt))

type_prop <- by_country_type %>%
  group_by(country) %>%
  mutate(prop = round(cnt / sum(cnt) * 100, 1)) %>%
  group_by(country) %>%
  summarise(total = sum(cnt), prop = prop, type = type) %>%
  as.data.frame() %>%
  top_n(20, wt = total)

custom_order <- type_prop %>%
  arrange(desc(ifelse(type == "Movie", prop, -prop))) %>%
  select(country) %>%
  array() %>%
  flatten() %>%
  unique()

p <- ggplot(type_prop, aes(y = factor(country, levels = custom_order), x = prop, fill = type)) +
  geom_bar(stat = "identity") +
  geom_text(
    aes(label = scales::percent(prop / 100)),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 3
  ) +
  labs(
    title = "Proportions of Movie and TV Show by Country",
    y = "Country",
    x = "Proportion (%)",
    fill = "Type"
  ) +
  scale_x_continuous(labels = scales::percent_format(scale = 1), limits = c(0, 100)) +
  scale_fill_manual(values = c("#221f1f", "#b20710")) +
  theme_minimal()
ggplotly(p)
```

### Distribution of netflix over years
```{r}

shared_country_accum <- SharedData$new(country_accum, key = ~country)

# Create a filter_slider for the 'year' variable
filter_slider_year <- filter_select(
  "year",
  "Current Year",
  shared_country_accum,
  ~year_added,
  multiple = F
  # column = ~year_added,
  # step = 1,
  # width = "50%",
)

# Plotly chart with crosstalk filter
choropleth_chart <- shared_country_accum %>%
  plot_ly(
    type = "choropleth",
    locations = ~country,
    locationmode = "country names",
    z = ~accum,
    color = ~accum,
    colors = "OrRd",
    colorbar = list(title = "Accumulated Sum"),
    text = ~ paste(country, "<br>Accumulated Sum: ", accum)
  ) %>%
  layout(inline = TRUE)

filter_slider_year
choropleth_chart
```

# Keywords {.storyboard}

```{r}
library(tidyverse)
library(purrr) # for functional programming
library(wordcloud2) # for creating word cloud
df <- read.csv("data/netflix_titles.csv", na.strings = c("", "NA"))
netflix_color <- colorRampPalette(c("#221f1f", "#b20710", "#e50914"))(10)
```



```{r}
COMMON_WORDS <- c("a", "in", "at", "be", "of", "the", "an", "to", "on", "he", "she", "and", "his", "with", "her", "for", "their", "when", "this", "from", "as", "is", "by", "after", "that", "who", "but", "into", "up", "they", "him", "out", "must", "are", "about", "it", "its", "while", "one", "them", "where", "has", "more", "over", "have", "off", "two", "s")

extract_words <- function(sentences) {
  strsplit(sentences, "\\s+") %>%
    flatten_chr() %>%
    map(str_remove_all, "[^a-zA-Z\\s]") %>%
    map(tolower) %>%
    flatten_chr() %>%
    discard(function(x) x == "") %>% # remove empty string
    discard(function(x) x %in% COMMON_WORDS)
}

word_cloud <- function(data) {
  words <- extract_words(data$description)
  occur <- table(words)
  occur <- sort(occur, decreasing = T)[1:50]
  ggwordcloud2(occur, color = netflix_color)
}
```

### The keywords of movies and TV show in Netflix from year 1944 to year 2000 (exclusive)  
```{r}
word_cloud(df %>% filter(1944 <= release_year & release_year < 2000))
```

### The keywords of movies and TV show in Netflix from year 2000 to year 2010 (exclusive)  
```{r}
word_cloud(df %>% filter(2000 <= release_year & release_year < 2010))
```

### The keywords of movies and TV show in Netflix from year 2010 to year 2020 (exclusive)  
```{r}
word_cloud(df %>% filter(2010 <= release_year & release_year < 2020))
```
